ANNO: The Anthropological Notation Ontology

### 2023-04-03 paper.tex
Expand paper and add some meeting notes.

\section{Developing ANNO}
The development of ANNO and its integration into \aw{} follows the \emph{three ontology method}~\citep{threeontologymethod} for ontology-based software engineering:
The \emph{domain ontology} describes the domain of skeletal anatomy.
The \emph{task ontology}
The General Formal Ontology (GFO)~\citep{gfo} is chosen as \emph{top-level ontology} and integrates the domain and task ontologies.

>>>>

\section{Developing ANNO}
The development of ANNO and its integration into \aw{} follows the \emph{three ontology method}~\citep{threeontologymethod} for ontology-based software engineering:
First, \emph{task ontology} is created as a conceptual model of \aw{}.
Second, the General Formal Ontology (GFO)~\citep{gfo} is chosen as \emph{top-level ontology} to provide a theoretical foundation.
Third, the \emph{domain ontology} is created that describes the domain of skeletal anatomy.
